%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {} % Affiliation/role
    {General Election 2015-17 Data Analysis} % Organization/group
    {} % Location
    {Oct - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {University project alongside 3 other colleagues over 7 week period.}
        \item{where we analysed the change in voting between the general elections of 2015 and 2017, and examined if there was any significance of a number of demographic variables and the voting statistics on the EU referendum.}
        \item{A concise project plan was created with objectives and potential pitfalls.}
        \item {We created a 6-page report of our findings in RMarkdown and a presentation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {} % Affiliation/role
    {Programming for Data Science Assignments} % Organization/group
    {} % Location
    {Oct - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {University module consists of statistical theory behind many data science practices.}
        \item {From simple bubblesort, mergesort algorithms, PCA, SVD, k-means clustering to Support Vector Machines and Artificial Neural Networks. }
        \item{We completed 3 assignments in pairs implementing the above in R. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {
    \href{https://www.kaggle.com/c/jigsaw-toxic-comment-classification-challenge}{https://www.kaggle.com/c/jigsaw-toxic-comment-classification-challenge}
    } % Affiliation/role
    {Kaggle Toxic comment Classification Challenge} % Organization/group
    {} % Location
    {March 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Tasked to build a model to detect different types of toxicity abusive comments. \href{https://www.kaggle.com/shonez}{Kaggle username: Shonez}}
        \item {I used a variety of NLP word processing such as bagofwords, Word2Vec and GloVe and formed a variety of different models, such as SVM, Na\"\i ve Bayes, and a Recurrent Neural Network using both R and Python. }
        \item{My result was a blend between multiple models and I came 1241st/4551 participants.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {
    \href{https://datahack.analyticsvidhya.com/contest/mckinsey-analytics-online-hackathon}{https://datahack.analyticsvidhya.com/contest/mckinsey-analytics-online-hackathon} }% Affiliation/role
    {McKinsey Healthcare Analytics 24h Online Hackathon} % Organization/group
    {} % Location
    {14th April 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Tasked to build a model predicting the likelihood of a patient to have a stroke.}
        \item {I used models including Na\"\i ve Bayes, Linear Regression, LASSO and a Neural Network in Python and R. (Workings can be found on my github)}
        \item{My final model was ridge regression optimised through grid search. My result was 204th/584 entries.}
      \end{cvitems}
    }
    
%---------------------------------------------------------

\end{cventries}
